Negative Types

### 2015-03-26 Univalence/outline.tex

@@

\paragraph*{FinSetCategory.} Defines the category of finite sets and
all functions between them. As stated on the nLab page, ``it is easy
(and thus common) to make \texttt{FinSet} skeletal; there is one
object for each natural number $n$ (including $n=0$), and a morphism
from $m$ to $n$ is an $m$-tuple $(f_0,\ldots,f_{m−1})$ of numbers
satisfying $0 \leq f_i < n$. This amounts to identifying $n$ with the
set $\{0,\ldots,n−1\}$.'' This structure will be a building block for
permutations (defined in \texttt{ConcretePermutation}).

>>>>

\paragraph*{SymmetricMonoidalCategory.} A definition of symmetric
monoidal categories.

@@

\paragraph*{SkFinSetCategory.} Defines the skeletal category of finite
sets and all functions between them. There is one object for each
natural number $n$ (including $n=0$), and a morphism from $m$ to $n$
is an $m$-tuple $(f_0,\ldots,f_{m−1})$ of numbers satisfying
$0 \leq f_i < n$. This structure will be a building block for
permutations (defined in \texttt{ConcretePermutation}).
